Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-05-10 Moltres.tex
all vars in delayed neutron equation have been previously handled

\begin{align}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'}
        \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} &- \nabla \cdot D_g 
        \nabla \phi_g + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G 
        \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - 
        \beta) \nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
\label{eq:neutrons}
        \intertext{where}
        v_g &= \mbox{speed of neutrons in group g} \\ 
        \phi_g &= \mbox{flux of neutrons in group g} \\ 
        t &= \mbox{time} \\ 
        D_g &= \mbox{Diffusion coefficient for neutrons in group g} \\ 
        \Sigma_g^r &= \mbox{macroscopic cross-section for removal of neutrons 
        from group g} \\ 
        \Sigma_{g'\rightarrow g} &= \mbox{macroscopic cross-section of 
        scattering from g' to g} \\ 
        \chi_g^p &= \mbox{prompt fission spectrum, neutrons in group g} \\ 
        G &= \mbox{number of discrete groups, g} \\ 
        \nu &= \mbox{number of neutrons produced per fission} \\ 
        \Sigma_g^f &= \mbox{macroscopic cross section for fission due to neutrons in group g} \\ 
        \chi_g^d &= \mbox{delayed fission spectrum, neutrons in group g} \\ 
        I &= \mbox{number of delayed neutron precursor groups} \\ 
        \lambda_i &= \mbox{average decay constant of delayed neutron precursors 
        in precursor group i} \\ 
        C_i &= \mbox{concentration of delayed neutron precursors in precursor 
        group i} . 
\end{align}

@@

\begin{align}
        \frac{\partial C_i}{\partial t} &= \sum_{g'= 1}^G \beta_i \nu 
        \Sigma_{g'}^f \phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u 
        C_i \label{eq:precursors}
        \intertext{where}
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
\end{align}

>>>>

\begin{align}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'}
        \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} &- \nabla \cdot D_g 
        \nabla \phi_g + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G 
        \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - 
        \beta) \nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
\label{eq:neutrons}
        \intertext{where}
        v_g &= \mbox{speed of neutrons in group g} \\ 
        \phi_g &= \mbox{flux of neutrons in group g} \\ 
        t &= \mbox{time} \\ 
        D_g &= \mbox{Diffusion coefficient for neutrons in group g} \\ 
        \Sigma_g^r &= \mbox{macroscopic cross-section for removal of neutrons 
        from group g} \\ 
        \Sigma_{g'\rightarrow g} &= \mbox{macroscopic cross-section of 
        scattering from g' to g} \\ 
        \chi_g^p &= \mbox{prompt fission spectrum, neutrons in group g} \\ 
        G &= \mbox{number of discrete groups, g} \\ 
        \nu &= \mbox{number of neutrons produced per fission} \\ 
        \Sigma_g^f &= \mbox{macroscopic cross section for fission due to neutrons in group g} \\ 
        \chi_g^d &= \mbox{delayed fission spectrum, neutrons in group g} \\ 
        I &= \mbox{number of delayed neutron precursor groups} \\ 
        \beta &= \mbox{delayed neutron fraction}\\
        \lambda_i &= \mbox{average decay constant of delayed neutron precursors 
        in precursor group i} \\ 
        C_i &= \mbox{concentration of delayed neutron precursors in precursor 
        group i} . 
\end{align}

@@

\begin{align}
        \frac{\partial C_i}{\partial t} &= \sum_{g'= 1}^G \beta_i \nu 
        \Sigma_{g'}^f \phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u 
        C_i \label{eq:precursors}
\end{align}
